---
output: 
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: true
    toc: false
title: \textbf{\textcolor{NavyBlue}{Protein Stability Report (Differential Scanning Fluorimetry)}}
date: "`r format(Sys.time(), '%F')`"
header-includes:
    - \usepackage{fancyhdr}
---

\fancyhf{}

\addtolength{\headheight}{0.4cm} 
\pagestyle{fancyplain}
\rhead{\includegraphics[height=1.2cm]{`r paste0(base_dir,"www/embl_logo.png")`}} 
\renewcommand{\headrulewidth}{0pt} 

\fontsize{14}{16}
\selectfont

\fancyfoot[CO,CE]{Automatic report provided by the SPC Facility, EMBL, Hamburg}
\fancyfoot[LE,RO]{\thepage}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{python, echo=FALSE,warning = FALSE}
import sys
```

```{r, echo=FALSE,warning = FALSE}
# Remove previous plots

fs1 <- list.files(".",pattern = "*signal.png")
fs2 <- list.files(".",pattern = "*derivative.png")
fs3 <- list.files(".",pattern = "*max_der.png")
fs4 <- list.files(".",pattern = "*unfolded_resultsPlot.png")
fs5 <- list.files(".",pattern = "*tmPlot.png")

for (fn in c(fs1,fs2,fs3,fs4,fs5))  { file.remove(fn) }

```

## Input 

File:                           `r input$FLf$name`   
Signal:                         `r input$which`          
Median Filter:                  `r input$median_filter`              
Minimum Temperature:            `r min(input$sg_range)`             
Maximum Temperature:            `r max(input$sg_range)`         
Normalization:                  `r switch(input$normalization_type,"Raw_signal"="Raw Signal","Divide_by_init_value"="Divide by initial value","MC_Normalization"="Max-Min Normalization","area_Normalization"="Area Normalization")`       

```{r, eval=input$report_include_signal,tidy=FALSE,results='asis',echo=FALSE}
cat("## Fluorescence Signal \n")
```

<br><br>

```{r, echo=FALSE,warning = FALSE,out.width = "100%",fig.align = "center",eval=input$report_include_signal,include=FALSE}

fluo_m <- make_df4plot(dsf$fluo,dsf$conditions,dsf$temps)

fluo_m <- fluo_m %>% group_by(cond_) %>% nest()

splitted_conditions <- split_vec(fluo_m$cond_,20)

i <- 0
plots <- list()
for (split_cond in splitted_conditions) {
  i <- i+1
  
  temp_df <- fluo_m %>% filter(cond_ %in% split_cond) %>% unnest(cols = c(data)) %>% ungroup()
  
  p <- plot_fluo_signal(temp_df,dsf$signal_type,input$plot_width,input$plot_height,
                        input$plot_type,input$plot_font_size,input$plot_axis_size)
  
  save_image(p, paste0(i,"signal.png"))

}
```

```{r, echo=FALSE,warning = FALSE,out.width = "100%",fig.align = "center",eval=input$report_include_signal}
files <- list.files(".",pattern = "*signal.png")
knitr::include_graphics(files)
```

```{r, eval=input$report_include_der,tidy=FALSE,results='asis',echo=FALSE}
cat("## First Derivative \n")
```

<br><br>
```{r, echo=FALSE,warning = FALSE,out.width = "100%",fig.align = "center",eval=input$report_include_der,include=FALSE}

fluo_m <- make_df4plot(dsf$derivative,dsf$conditions,dsf$temps)
fluo_m <- fluo_m %>% group_by(cond_) %>% nest()

splitted_conditions <- split_vec(fluo_m$cond_,20)

i <- 0
for (split_cond in splitted_conditions) {
  i <- i+1
  
  temp_df <- fluo_m %>% filter(cond_ %in% split_cond) %>% unnest(cols = c(data)) %>% ungroup()
  
  p <- plot_fluo_signal(temp_df,"First derivative",input$plot_width,input$plot_height,
                        input$plot_type,input$plot_font_size,input$plot_axis_size)
  
  
  save_image(p,paste0(i,"derivative.png"))
}
```

```{r, echo=FALSE,warning = FALSE,out.width = "100%",fig.align = "center",eval=input$report_include_der}
files <- list.files(".",pattern = "*derivative.png")
knitr::include_graphics(files)
```

```{r, eval=input$report_include_max_der,tidy=FALSE,results='asis',echo=FALSE}
cat("## Maxium of Derivative \n")
```

<br><br>
```{r, echo=FALSE,warning = FALSE,out.width = "100%",fig.align = "center",eval=input$report_include_max_der,include=FALSE}

splitted_conditions <- split_vec(1:length(dsf$conditions),20)

i <- 0
for (split_cond in splitted_conditions) {
  i <- i+1
  
  p <-  generate_max_der_plot(dsf$tms_from_deriv[split_cond],dsf$conditions[split_cond],
                             input$plot_width, input$plot_height, 
                             input$plot_type,input$plot_font_size,input$plot_axis_size)
  
  save_image(p,paste0(i,"max_der.png"))
}
```

```{r, echo=FALSE,warning = FALSE,out.width = "100%",fig.align = "center",eval=input$report_include_max_der}
files <- list.files(".",pattern = "*max_der.png")
knitr::include_graphics(files)
```

```{r, eval=input$report_include_fitted_params_table,tidy=FALSE,results='asis',echo=FALSE}
cat("## Fitted Parameters \n")
```

<br><br>
```{r, echo=FALSE,warning = FALSE,out.width = "100%",fig.align = "center", eval=input$report_include_fitted_params_table}

knitr::kable(
  get_sorted_params_table(dsf$params_all,dsf$fitted_conditions,global_chunck_n,dsf$params_name,input$sort_table_parameter))

```

```{r, eval=input$report_include_fitted_params_errors_table,tidy=FALSE,results='asis',echo=FALSE}
cat("## Fitted Parameters Relative Errors (%) \n")
```

<br><br>

```{r, echo=FALSE,warning = FALSE,out.width = "100%",fig.align = "center", eval=input$report_include_fitted_params_errors_table}

table <- get_sorted_params_table_errors(dsf$errors_percentage_all,dsf$fitted_conditions,dsf$params_name,input$sort_table_parameter)

last_col <- length(colnames(table))-1

colnames(table)[1:last_col] <- sapply(colnames(table)[1:last_col], function(x) {
  strsplit(x,"/")[[1]][2]
})

knitr::kable(table)

```

```{r, eval=input$report_include_fitting_plots,tidy=FALSE,results='asis',echo=FALSE}
cat("## Fitting Plots \n")
```

<br><br>
```{r, echo=FALSE,warning = FALSE,out.width = "100%",fig.align = "center" , eval=input$report_include_fitting_plots}

total_plots <- ceiling(length(dsf$fitted_conditions)/global_chunck_n)

for (selected in 1:total_plots) {
  real_data  <- fluo_fit_data()$fluo_fit_real
  model_data <- fluo_fit_data()$fluo_fit_pred
  grid.draw(plot_fluorescence_fit(real_data,model_data,selected,TRUE))
}

```

```{r, eval=input$report_include_results_plots,tidy=TRUE,results='asis',echo=FALSE}
cat("## Results Plot \n")

l1 <- paste0("For all fitted parameters: (Standard_deviation / value) * 100 < 50: "     ,input$sd_factor_bool, "\n")
l2 <- paste0("Baseline separation factor > 0.5       (Only for Two State models): "     ,input$bs_factor_bool, "\n")
l3 <- paste0("Estimated parameters far from fitting bounds:                       "     ,input$far_from_bounds,"\n")
  
cat(c(l1,l2,l3),sep="\n")

```

<br><br>

```{r, echo=FALSE,warning = FALSE,eval=input$report_include_results_plots,include=FALSE}

selected_indexes <- filter_conditions()

if (any(selected_indexes) & input$model_selected == "EquilibriumTwoState") {
  dh_position <- which(dsf$params_name == "dHm")  
  dhs <- sapply(dsf$params_all, function(x) x[dh_position])
  
  tm_position <- which(dsf$params_name == "Tm")  
  tms <- sapply(dsf$params_all, function(x) x[tm_position])
  
  dhs               <- dhs[selected_indexes]
  tms               <- tms[selected_indexes]
  fitted_conditions <- dsf$fitted_conditions[selected_indexes]
  t_onset           <- dsf$T_onset[selected_indexes]
  
  splitted_conditions <- split_vec(1:length(fitted_conditions),20)
  
  i <- 0
  for (split_cond in splitted_conditions) {
    
    i <- i+1
    
    fig <- generate_fractions_plot(
      dhs[split_cond],tms[split_cond],fitted_conditions[split_cond],t_onset[split_cond],
      input$plot_width_results,input$plot_height_results,input$plot_type_results,
      input$plot_font_size_results,input$plot_axis_size_results,FALSE)
    
    save_image(fig,paste0(i,"fraction_unfolded_resultsPlot.png"))
}

}

```

```{r echo=FALSE, out.width = "100%", fig.align="center", warning=FALSE, eval=(length(list.files(".",pattern = "*resultsPlot.png"))>0)}

files <- list.files(".",pattern = "*resultsPlot.png")
knitr::include_graphics(files)

```

```{r, echo=FALSE,warning = FALSE,eval=input$report_include_results_plots,include=FALSE}

if (any(selected_indexes) & (input$model_selected %in% c("EquilibriumTwoState","EmpiricalTwoState"))) {

  tm_position <- which(dsf$params_name == "Tm")  
  tms <- sapply(dsf$params_all, function(x) x[tm_position])
  
  tms               <- tms[selected_indexes]
  fitted_conditions <- dsf$fitted_conditions[selected_indexes]
  
  splitted_conditions <- split_vec(1:length(fitted_conditions),20)
  i <- 0
  for (split_cond in splitted_conditions) {
    
    i <- i+1
    
    fig <- generate_tm_plot(tms[split_cond],fitted_conditions[split_cond],
                        input$plot_width_results, input$plot_height_results, 
                        input$plot_type_results,input$plot_axis_size_results)
    
    save_image(fig,paste0(i,"tmPlot.png"))
}
  
}

```

```{r echo=FALSE, out.width = "100%", fig.align="center", warning=FALSE, eval=(length(list.files(".",pattern = "*tmPlot.png"))>0)}
files <- list.files(".",pattern = "*tmPlot.png")
knitr::include_graphics(files)

```
  

